---
title: "615 final project"
author: "Xiangliang Liu"
date: "December 9, 2018"
output: pdf_document
---

##Introduction:

*Watching movie is always a good recreation for people who live under a stressful life style. However, we are constantly facing fake revenue record regarding to the newly released movie. This project will mainly focus on exploring some fundamental information about 5000 movies in the dataset called "The Movie Data Base". Specifically, we will conduct Benford analysis on Budget, revenue and popularity varibles in the dataset.  *

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data visualization and EDA:

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Load package
library(benford.analysis)
library(readr)
library(dplyr)
library(tidyverse)
library(kableExtra)
library(jsonlite) 
library(RColorBrewer)
library(wordcloud)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Read in the data and data cleaning:
tmdb <- read_csv("tmdb_5000_movies.csv")

#Use dplyr to specify the columns
movie <- tmdb %>%
  select(budget, genres, id, popularity, title, production_companies, production_countries, revenue, vote_average, vote_count)%>%
  filter(budget>0 & revenue>0)

#summary of the data
summary(movie)

#Convert JSON format into data frame
#genre data:
genre_data <-movie %>% 
  filter(nchar(genres) > 2) %>% 
  mutate(js = lapply(genres, fromJSON)) %>% 
  unnest(js) %>% 
  select(genre = name) 

#country data:
country_data <- movie %>%
  filter(nchar(production_countries)>2) %>%     
  mutate(cntry=lapply(production_countries,fromJSON)) %>%  
  unnest(cntry) %>% 
  select( id,production_countries=name)

country_data$production_countries<- recode(country_data$production_countries,"United States of America" = "USA", "United Kingdom" = "UK")
```

###EDA
####Check the distribution plot with varible budget, revenue, popularity and number of count
```{r echo=FALSE}

ggplot(movie,aes(x = budget)) + 
  geom_histogram(fill ="sky blue", color = "black")+
  ggtitle("The distribution of budget")

ggplot(movie,aes(x = revenue)) + 
  geom_histogram(fill ="sky blue", color = "black")+
  ggtitle("The distribution of revenue")

ggplot(movie,aes(x = popularity)) + 
  geom_histogram(fill ="sky blue", color = "black")+
  ggtitle("The distribution of popularity")

ggplot(movie,aes(x =vote_count )) + 
  geom_histogram(fill ="sky blue", color = "black")+
  ggtitle("The distribution of number of vote")

```

####Most popular movies
```{r}
#Top 20 most popular movie
pop<-movie%>%
  select(title, popularity)%>%
  arrange(desc(popularity))
#chose the top 20 rows of the pop dataset
pop <- pop[c(0:20),]

ggplot(data = pop, aes(x=reorder(title, popularity ), y=popularity)) +
        geom_col(fill="sky blue") + 
        coord_flip() +
        labs(x = "", y=" Popularity")+ 
        geom_text(aes(label = popularity))+ 
        ggtitle("Top 20 most popular movie")

```

*The plot showing above indicates the top 20 most popular movie in the movie data base. The movie Minions is the movie with biggest popularity*


###Create a genre wordcloud
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Show the distribution Genre
genre_data %>% 
  group_by(genre) %>% 
  count() %>%
  ggplot(aes(x=reorder(genre, n), y=n)) +
  geom_col(fill="sky blue") + coord_flip() +
  labs(x = "", y = "Number of movies") + 
  geom_text(aes(label = n))

#Generate a Wordcloud
genre_data %>%
  group_by(genre)%>%
  count(genre)%>%
  with(wordcloud(genre, n, max.words = 19, rot.per = 0.35, colors = brewer.pal(2,"Dark2"), scale = c(8,.2)))
```
*The wordclouds gives us a general idea about which genres have the largest proportion. It turns out that Drama, Comedy and Thriller are the top 3 genres with highest number of movies*


###mapping with production countries
```{r echo=FALSE, warning=FALSE}
#mapping
map.world = map_data("world")

country<-country_data %>%
  group_by(production_countries)%>%
  count(production_countries)%>%
  arrange(desc(n))%>%
  filter(n >20)

ggplot(data= country, aes(x = reorder(production_countries, n), y = n, fill = production_countries))+ 
  geom_col() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("the distribution of movies in different countries")+ 
  geom_text(aes(label = n),position = position_dodge(0.9),vjust = 0) + 
  coord_flip()+
  labs(x = "", y ="number of movies")
 #from the plot we can see USA has the most number of movie in the dataset.


map.world_joined <- left_join(map.world, country, by = c('region' = 'production_countries'))
map.world_joined <- map.world_joined %>% mutate(fill_flg = ifelse(is.na(n),F,T))

#make the plot about the world map
ggplot() +
  geom_polygon(data = map.world_joined, aes(x = long, y = lat, group = group, fill = fill_flg)) +
  scale_fill_manual(values = c("#CCCCCC","#e60000")) +
  labs(title = "Countries with more than 20 movies") +
  theme(text = element_text(family = "Gill Sans", color = "#FFFFFF")
        ,panel.background = element_rect(fill = "#444444")
        ,plot.background = element_rect(fill = "#444444")
        ,panel.grid = element_blank()
        ,plot.title = element_text(size = 30)
        ,plot.subtitle = element_text(size = 10)
        ,axis.text = element_blank()
        ,axis.title = element_blank()
        ,axis.ticks = element_blank()
        ,legend.position = "none")
```
##Bnford analysis:
```{r}
#benford analysis base on diferent variables.
movie_b <- benford(movie$budget)
plot(movie_b)
movie_b
```
*as we can see from the distrbution and summary of the Benfore test, the budget data in movie dose not follow Benford distribution. A lot of lines exceed the red line threshold. Also the p-value in the summary is less than 0.05, which reject the htpothesis that the distribution follow benford distribution. *

```{r}
movie_r <- benford(movie$revenue)
plot(movie_r)  
movie_r
```
*The benford test on revenue indicates p-value is 0.2925 > 0.05, so do not reject the hypothesis that the distribution follow Benford distribution. This is result is what *

```{r}
movie_p <- benford(movie$popularity)
plot(movie_p)  
movie_p
```
*As for the variable popularity, the p-values from Chi-squared test is 0.0001389, which is less than 0.05. So we do reject the hypothesis that the distribution follow Benford distribution*

## Conclusion:
###insights and findings:
*We found the budget numbers do not significantly follow Benford analysis. The budget that start with 50 and 20 have the highest deviation. This result does make sense, because when people decide to make a movie or approve a movie, they never specific the budget to a unit digit. For instant, the number could be 500 million or 200 million dollars*

###limitation:
*There are a few limitations about the benford analysis. We can only test whether the data follow Benford distribution. After that, even if we know the data does not follow the distribution, we still have to do more research on the data to explore whether there are some frauds in the data.*

###Reference:
https://www.kaggle.com/tmdb/tmdb-movie-metadata


